---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HLManalysis

<!-- badges: start -->
<!-- badges: end -->

This function is a wrapper for the [dplyr::summarize()] function from the dplyr package. The function is fortified to handle the missing values (NA), and it can provide a summary table with many descriptive statistics for a variable grouped by a specify categorical variable. In this case, this function can be used in multilevel models, and provide the statistics for the level 2 units (e.g. the groups).



## Installation

HLManalysis is not yet no CRAN. But, you can download it from this repository using the follwoing R command:


``` r
devtools:: install_github("Guanyu0001/HLManalysis")
```

## Example

First example is about `mtcars`, which was extracted from the 1974 *Motor Trend* US magazine. The "am" is the transmission (0 = automatic, 1 = manual), "mpg" is the Miles/(US) gallon. Here we can get the descriptive statistics Miles/(US) gallon between automatic and manual transmission. 

```{r example}
library(HLManalysis)
level2summarize(mtcars, am, mpg)
```

Second example is to show the requirement of each argument. For the parameter a (e.g., grouping variable), both numeric and factor variables work. To make the function more robust and user-friendly, this function does not ask user to choose a categorical variable. For the parameter b (e.g., the dependent variable or outcome), a numeric variable is required; Otherwise, all the descriptive statistics does not make sense.

```{r, error=T}
library(HLManalysis)
# parameter a can be numeric or factor
a <- as.factor(c(rep(1, 10), rep(2, 10)))
b <- as.numeric(c(rep(1, 10), rep(-1, 10))) # a as numeric
data1 <- data.frame(a, b)
level2summarize(data1, a, b)

a <- as.numeric(c(rep(1, 10), rep(2, 10)))
b <- as.numeric(c(rep(1, 10), rep(-1, 10))) # a as factor
data1 <- data.frame(a, b)
level2summarize(data1, a, b)

# parameter b should be numeric
a <- as.factor(c(rep(1, 10), rep(2, 10)))
b <- as.factor(c(rep(1, 10), rep(-1, 10))) # b as factor
data1 <- data.frame(a, b)
level2summarize(data1, a, b)

a <- as.factor(c(rep(1, 10), rep(2, 10)))
b <- as.numeric(c(rep(1, 10), rep(-1, 10))) # b as numeric
data1 <- data.frame(a, b)
level2summarize(data1, a, b)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

